Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
"at the time" -> "at present" and "many" -> "some" in missing algos
break long sentence about FeatureUnion and move some stuff around

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that concatenates their outputs,
in the sense that a union of transformers that map inputs having $d$ features
to $d'$ and $d''$ features, respectively,
is a transformer that maps its $d$ input features to $d' + d''$ features
by calling its underlying transformers in parallel.
From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers.

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selecting the 10 best of those features according to an ANOVA test
and then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
As the above example shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.

@@

Although it is coming close to a 1.0 release, \sklearn is by no means finished.
At the time, it does not support many classical machine learning tasks. Among
others, missing features include neural networks, ensemble meta-estimators for
bagging or subsampling strategies, or missing value completion algorithms.
Topics like structured prediction or reinforcement learning are however
considered off-topic for the project, since they would require quite different
data representations and API.

>>>>

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that concatenates their outputs.
I.e., a union of transformers that map inputs having $d$ features
to $d'$ and $d''$ features, respectively,
is a transformer that maps its $d$ input features to $d' + d''$ features
by calling its underlying transformers in parallel.
From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers.

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selecting the 10 best of those features according to an ANOVA test
and then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}

@@

Although it is coming close to a 1.0 release, \sklearn is by no means finished.
At present, it does not support some classical machine learning tasks. Among
others, missing features include neural networks, ensemble meta-estimators for
bagging or subsampling strategies, or missing value completion algorithms.
Topics like structured prediction or reinforcement learning are however
considered off-topic for the project, since they would require quite different
data representations and API.
